Keeping it even: maintaining evenly distributed temperatures within a two-dimensional bathtub

### 2016-02-01 article/main.tex
Closer to the final draft

\title{Numerical simulation of two-dimensional heat convection-diffusion with
ellipsoid geometries}

@@

The basis of this paper is to develop a model that permits a person to maintain their preferred temperature of the bathtub water while minimizing water consumption.

@@

@@

>>>>

\title{Keeping it even: maintaining evenly distributed temperatures within a
two-dimensional bathtub}

@@

The avid bather faces the constant struggle in balancing her ability to relax in
the bathtub and in keeping an evenly distributed water temperature within the
tub. For such a bather a quality bath is a necessity. Necessity, the mother of
invention, requires that quality be sought after and maximized---the bather
should need to worry as little as possible about the quality of the temperature
distribution in the tub. To help our bather, we seek to give a precise
determination of quality and pose a question in whose answer provides the best
such quality. Yet living in a world of scarce resources demands attention
towards the cost of our decisions. Our underlying quest for quality needs
temperament from reality, and we shall formulate the problem as a trade-off
between these competing camps.

In this work, we begin by developing a model for the evolution of heat in a
bathtub. Heat travels through a fluid by two means: diffusion and convection.
The diffusion process refers to the natural spread of heat from high-temperature
peaks to low-temperature valleys. This process is fundamentally spatial and
occurs even in the context of a stationary fluid. The convection process, by
contrast, refers to the spread of heat subject to a moving fluid. Heat can flow
with a fluid to spread along the direction the fluid travels; this process helps
to explain the behavior of ocean conveyor belts and hurricanes. In order to
optimize the distribution of heat, we need to understand how heat evolves. This
will be the primary scope of our paper.

Our work proceeds as follow. Section 2 describes the high-level view of the
computational model for simulating the evolution of heat in a bathtub in the
context of both a stationary and moving fluid. It also outlines the numerical
methods we will use in order to approximate the underlying diffusion and
convection processes. We also propose, but do not solve, the bather's
optimization problem. Section 3 provides the results of our initial

@@

\subsection{Heat diffusion in a stationary fluid}

@@

\subsection{Nonstationarity and numerical stability}
